---
title: "Cleaning DistillerSR"
author: "Brady Johnston"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: show
    theme: united
    highlight: pygments
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup-packages, results=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(remedy)

```

## Level 4 Data Cleaning

The output from distiller isn't nice, so we need to clean it up a bit before proceeding with analysis. Download the Distiller data from datarama. 

for level 4 just check the level 4 box and save as .csv

for level 3 from the "reference display options" also select:\
- Author\
- Title\
- DOI\
- Issue\
- Journal\
- Pages\
- Volume\

find the files in your downloads and then save them in the VC_scoping_review/data folder as "level_3.csv" and level_4.csv"

### Reading the raw `.csv` downloaded from DistillerSR.

```{r read-raw}

# have to have the guess_max increased or some values are missed because
# read_csv incorrectly guesses some columns to be logical.

raw_level_4 <- read_csv(
  file      = here("data", "level_4.csv"), 
  guess_max = 10000
  )

```

As we can see, the raw `.csv` is a table with `r ncol(raw_level_4)` columns and `r nrow(raw_level_4)` rows.
This is because each possible answer for a question in Distiller is given it's own column, even when the answer is for the same question.


We can now apply this same process to the rest of the *very wide* table to make it more manageable, using the great `purrr::reduce()` function.

### Combining All Columns

Into the function we feed a `tibble` that contains two columns, the `new_name` that will make the name for the newly combined column, and the `contains_string` which will be the string that is used to select the required columns that will be combined.

```{r apply-all}

# new names and selection strings
selection_names <- tribble(
  ~new_name,              ~contains_string,
  "age_exp",               "4. Age", 
  "age_exp_infant",        "(age <18) [Exposure]", 
  "risk",                  "Is there a special risk population in", 
  "risk_special",          "-> Special risk – ",
  "risk_maternal",         "-> Maternal special risk - ",
  "risk_paternal",         "-> Paternal special risk - ",
  "risk_compartor_group",  "Comparator Group (to the special risk group)",
  "chem_name_ref",         "5a. Please", 
  "chem_name_shiny",       "5b. Please provide the chemical name found in the ShinyApp", 
  "age_health",            "6. Age", 
  "age_health_infant",     "(age <18) [Outcome measure]",
  "health_outcomes_paper", "7a. Please",
  "health_outcomes_shiny", "7b.",
  "gender",                "Gender of population",
  "population",            "individuals/pairs/families?",
  "study_design",          "8. Please indicate the study design",
  "multiple_exposures",    "multiple exposures measured",
    # "maternal_risk", "Maternal"
)

# cleaning and compression of the overly wide columns
cleaned_level_4 <- raw_level_4 %>%
  select(!contains("exclusion")) %>%
  purrr::reduce2(
    .x = selection_names$new_name,
    .y = selection_names$contains_string,
    .f = function (data, x, y) {
      unite(
        data = data,
        col = !!x,
        contains(y),
        sep = "_",
        na.rm = TRUE
      )
    },
    .init = .
  )

```

### cleaning up entries

There were some entries in distiller that are not matching in shiny, such as\
- All pcb congeners\
- Measures of neurodevelopment in infants > 1 month and <1 year\
- Disorders of newborn related to fetal growth or fetal nutrition


```{r cleaning up level 4}
cleaned_level_4 <- janitor::clean_names(cleaned_level_4)

#we need to replace any part of the string that has "All PCB Congeners" by individuals congeners
cleaned_level_4 <- cleaned_level_4 %>%
   mutate(chem_name_shiny = str_replace(chem_name_shiny, 
                                        "All PCB Congeners", 
                                        paste("PCB", 1:209, collapse = "_")
                                        )
          )

# Use this to find specific chemicals in the distiller output
# cleaned_level_4 %>% 
#   select(refid, 
#          chem_name_shiny) %>%
#   filter(str_detect(chem_name_shiny, 
#                     "tetradecyl")
#          ) %>%
#   print(n = 5)

#####################
# here we change the issue with > and <, as well as an updated outcome in the mastersheet

# Use this to find specific health outcomes in the distiller output
# cleaned_level_4 %>% 
#   select(refid, 
#          health_outcomes_shiny) %>%
#   filter(str_detect(health_outcomes_shiny, 
#                     "Measures of neurodevelopment in infants &gt; 1 month and &lt;1 year other than measures of general cognitive performance")
#          ) %>%
#   print(n = 5)



cleaned_level_4 <- cleaned_level_4 %>%
   mutate(health_outcomes_shiny = str_replace(health_outcomes_shiny, 
                                        "infants &gt; 1 month and &lt;1 year", 
                                        "infants > 1 month and <1 year"
                                        ),
          health_outcomes_shiny = str_replace(health_outcomes_shiny, 
                                        "Disorders of newborn related to slow fetal growth or fetal malnutrition", 
                                        "Disorders of newborn related to fetal growth or fetal nutrition"
                                        )
          )

```

## Level 3 Data Cleaning

Lets do a similar cleaning process on the level 3 form, which contains some metadata about the paper itself.

```{r cleaning-form-a}

raw_level_3 <- read_csv(
  file = here("data", "level_3.csv"), 
  guess_max = 10000
  )



cleaned_level_3 <- raw_level_3 %>%
    unite(
    "country_investigated",
    contains("Country of the investigated population"), 
    sep = "_",
    na.rm = TRUE
    ) %>%
  unite(
    col = "reason_for_exclusion", 
    contains("Reason for exclusion:"), 
    sep = "_", 
    na.rm = TRUE
    ) %>% 
  rename(
    country_first_auth = contains("2. What is the country"), 
    country_last_author = contains("3. What is the country"), 
    year = contains("Paper Information\n1. Which year"),
    exclusion = contains("Exclusion\nPlease ensure")
    ) %>%
  mutate(citation = str_glue("{Author}, {Title} ({year}) {Journal}. {Volume}, {Issue}, {Pages}. DOI: {DOI}")
         ) 

cleaned_level_3 <- janitor::clean_names(cleaned_level_3)

```

### combining level 3 and 4 data

``` {r combining 3 and 4}

cleaned_full_data <- cleaned_level_4 %>%
                        left_join(cleaned_level_3, 
                                  by = c("refid" = "refid")
                                  ) %>%
                        filter(exclusion == "Continue"
                               ) %>%
                        drop_na(l4_0_child_form_b_k)   
```

### Now we add the relevant data for the mastersheet to the dataframe

``` {r adding the indices}
chem_index <- readxl::read_excel(here("data", "final_chem_shiny.xlsx"), sheet = "Additives") %>% janitor::clean_names()

poly_index <- readxl::read_excel(here("data", "final_chem_shiny.xlsx"), sheet = "Polymers"
                                 ) %>%  
  janitor::row_to_names(row_number = 1) %>%
  janitor::clean_names()

hom_index  <- readxl::read_excel(here("data", "final_health_shiny.xlsx"), sheet = "Health classes") %>% janitor::clean_names()


##################
# naphtphalene test

# chem_index %>% 
#   select(x3) %>% 
#   filter(str_detect(x3, "naphthalenes"))
# 
# 
# ###############

chem_index <- chem_index %>% 
  filter(included_in_shiny == "y") %>%
  select(additive_identification,
         "chem_name_shiny"   = x3,
         "cas"               = x6,
         "smiles"            = x8,
         "inchl"             = x10,
         "inchlkey"          = x11,
         "plasticiser"       = additive_function,
         "flame_retardant"   = x29,
         "pfas"              = x31,
         "class"             = x27,
         #"class2"            = x22,
         #"class3"            = x23,
         "gen_function"      = x12,
         "sector"            = x14,
         "production_volume" = x19,
         "level_of_concern"  = x21,
         "source1"           = x102,
         "source2"           = x103) %>%
  filter(!is.na(class))
  

####### consolidating sources ########
chem_index_c <- chem_index %>% 
  unite("source",
        source1, source2,
        sep    = "; ",
        remove = T,
        na.rm  = T) %>% 
  separate_rows(source,
                sep = "; ") %>% 
  unique() %>% 
  group_by_at(vars(-source)) %>% 
  summarize(source = paste0(source, collapse = "; ")
            )

# source_names <- chem_index_c %>% 
#   separate_rows(source,
#                 sep = "; ") %>% 
#   group_by(source) %>% 
#   count()  

#writexl::write_xlsx(source_names, here("Output", "chem_sources.xlsx"))
# source_index <- readxl::read_excel(here("Output", "chem_sources_index1.xlsx")) %>% janitor::clean_names()
# 
# source_names2 <- chem_index_c %>% 
#   separate_rows(source,
#                 sep = "; ") %>%
#   left_join(source_index,
#             by = c("source" = "old_source")) %>% 
#   mutate(source = new_source) %>% 
#   select(-new_source) %>% 
#   separate_rows(source,
#                 sep = "; ") %>% 
#   group_by(source) %>% 
#   count()  

#writexl::write_xlsx(source_names2, here("Output", "chem_sources2.xlsx"))  
source_index2 <- readxl::read_excel(here("Output", "chem_sources2_index.xlsx")) %>% janitor::clean_names()   

chem_index_c <- chem_index_c %>% 
  separate_rows(source,
                sep = "; ") %>%
  left_join(source_index2,
            by = c("source" = "source_old")) %>% 
  mutate(source = source_new) %>% 
  select(-source_new) %>% 
  separate_rows(source,
                sep = "; ") %>% 
  unique() %>% 
  group_by_at(vars(-source)) %>% 
  summarize(source = paste0(source, collapse = "; ")
            )


###

chem_index_c2 <- chem_index_c %>% 
  mutate(pfas = ifelse(!is.na(pfas),
                       "PFAS",
                       pfas)) %>% 
  unite("add_function",
        plasticiser, flame_retardant, pfas, 
        sep = "; ",
        remove = T,
        na.rm = T) %>% 
  mutate(production_volume = case_when(production_volume == "missing" ~ "No data available",
                                       is.na(production_volume)       ~ production_volume,
                                       TRUE                           ~ production_volume),
         level_of_concern = case_when(level_of_concern == "mising"    ~ "No data available",
                                       is.na(level_of_concern)        ~ level_of_concern,
                                       TRUE                           ~ level_of_concern),
         source = str_replace_all(source,
                                  "; NA",
                                  "")
         )


# unique source check
chem_index_c2 %>% 
  group_by(source) %>% 
  count() 


###############

poly_index <- poly_index %>%
  select("chem_name_shiny"       = polymer_name_or_class,
         "cas"                   = cas_number,
         "crow"                  = crow_link,
         "source_1"              = source_1_wypych,
         "source_2"              = source_2_kolzenburg,
         "source_3"              = source_3_braun,
         "source_4"              = source_4_salamone,
         "source_5"              = source_5_ravve,
         "source_6"              = source_6_lither
         ) %>%
  mutate(additive_identification  = NA,
         class                    = "Polymers",
         smiles                   = NA,
         inchl                    = NA,
         inchlkey                 = NA,
         #class2                  = NA,
         #class3                  = NA,
         add_function             = NA,
         gen_function             = NA,
         sector                   = NA,
         production_volume        = NA,
         level_of_concern         = NA
         )
 
poly_index_c <- poly_index %>% 
  mutate(crow = ifelse(!is.na(crow),
                       "https://www.polymerdatabase.com/",
                       crow),
         source_1 = ifelse(!is.na(source_1),
                       "Wypych (2016)",
                       source_1),
         source_2 = ifelse(!is.na(source_2),
                       "Koltzenburg et al (2017)",
                       source_2),
         source_3 = ifelse(!is.na(source_3),
                       "Braun et al (2012)",
                       source_3),
         source_4 = ifelse(!is.na(source_4),
                       "Salamone (1996)",
                       source_4),
         source_5 = ifelse(!is.na(source_5),
                       "Ravve et al (2012)",
                       source_5),
         source_6 = ifelse(!is.na(source_6),
                       "Lithner et al (2011)",
                       source_6)
         ) %>% 
  unite("source",
        crow, source_1, source_2, source_3, source_4, source_5, source_6,
        sep    = "; ",
        remove = T,
        na.rm  = T)

# chem_supp <-   chem_supp %>% 
#   mutate(class2 = "")


chem_index_full <- rbind(chem_index_c2, poly_index_c)  
#chem_index <- rbind(chem_index, chem_supp %>% mutate(class2 = "",
#                                                     class3 = ""))  


cleaned_full_data <- cleaned_full_data %>%
          separate_rows(chem_name_shiny, 
                        sep = "_") %>%
          left_join(chem_index_full, 
                    by = c("chem_name_shiny" = "chem_name_shiny")) %>%
          separate_rows(health_outcomes_shiny, 
                        sep = "_") %>%
          left_join(hom_index, 
                    by = c("health_outcomes_shiny" = "display"))


found_chem <- cleaned_full_data %>% 
  select(chem_name_shiny) %>%
  unique()%>%
  unlist


chem_index2 <- chem_index_full %>%
  mutate(presence = ifelse(chem_name_shiny %in% found_chem,
                           "found",
                           "not found")
         )





```
## Quality control

here we run some test to see if there are any issues with data merging.

``` {r Quality control}

######## Comparator group not selected #######
cleaned_full_data %>%
  select(
    refid,
    risk,
    risk_compartor_group
  ) %>%
  unique() %>%
  drop_na() %>%
    filter(risk == "Yes" & risk_compartor_group == "") %>%
  select(refid) %>%
  paste()

####### exposure and health outcome is prenatal individual ########
cleaned_full_data %>%
  select(refid,
         age_exp,
         age_health,
         population) %>%
  unique() %>%
  filter(age_health == "Prenatal (&lt;0)" &
         age_exp == "Prenatal (&lt;0)") %>%
  select(refid) %>%
  paste()

########### multiple genders #######
cleaned_full_data %>%
  select(
    refid,
    gender,
    population
    ) %>%
  filter(population == "Individual(s)") %>%
  select(refid,
         gender) %>%
  unique() %>%
  group_by(refid) %>% 
  filter(n()>1)   %>%
  select(refid)   %>%
  unique() %>%
  paste()


###### multiple chem classes, not multiple_exp selected ####
cleaned_full_data %>%
  select(
    refid,
    class,
    multiple_exposures,
    study_design
    ) %>%
  filter(multiple_exposures != "'multiple exposures measured&rsquo; (tick if &gt;1 plastic type or chemical class, whether on the &lsquo;included&rsquo; list or not)" &
           study_design != "Experimental study without a control/comparison group (patch testing)") %>%
  select(refid,
         class) %>%
  unique() %>%
  group_by(refid) %>% 
  filter(n()>1) %>%
   select(refid) %>%
  unique() %>%
  paste()

cleaned_full_data %>%
  select(refid) %>% 
  filter(refid == "2007895660") %>%
  unique() %>%
  paste()


#### HoM mismatch ####

cleaned_full_data %>%
  select(
    refid,
    level0,
    health_outcomes_shiny
    ) %>%
  unique() %>%
  filter(is.na(level0)) %>%
  paste()

 cleaned_full_data %>%
  select(
    level0,
    health_outcomes_shiny
    ) %>%
  
  filter(is.na(level0)) %>%
  select(health_outcomes_shiny) %>%
  unique() %>% 
   paste()

##### Chem mismatch ####
cleaned_full_data %>%
  select(
    refid,
    class,
    chem_name_shiny
    ) %>%
  unique() %>%
  filter(is.na(class)) %>%
  select(refid) %>%
  paste()


cleaned_full_data %>%
  select(
    class,
    chem_name_shiny
    ) %>%
  filter(is.na(class)) %>%
  select(chem_name_shiny) %>%
  unique()
 


##### Years mismatch ####
cleaned_full_data %>%
  select(
    refid,
    year) %>%
  unique() %>%
  group_by(refid) %>%
  filter(n()>1)   %>%
  select(refid)   %>%
  unique() %>%
  paste()

##### poplation mismatch ####
cleaned_full_data %>%
  select(
    refid,
    country_investigated) %>%
  unique() %>%
  group_by(refid) %>%
  filter(n()>1)   %>%
  select(refid)   %>%
  unique() %>%
  paste()

cleaned_full_data %>%
  select(
    refid,
    country_first_auth) %>%
  unique() %>%
  group_by(refid) %>%
  filter(n()>1)   %>%
  select(refid)   %>%
  unique() %>%
  paste()

cleaned_full_data %>%
  select(
    refid,
    country_last_author) %>%
  unique() %>%
  group_by(refid) %>%
  filter(n()>1)   %>%
  select(refid)   %>%
  unique() %>%
  paste()

cleaned_full_data %>%
  select(year,
    refid,
    chem_name_shiny
    ) %>%
  unique() %>%
  filter(str_detect(chem_name_shiny, "Bisphenol F")) %>%
  group_by(year) %>%
  count()

```

```{r writing full dataframe}
#write_csv(cleaned_level_4, here("cleaned_data", str_glue("{Sys.Date()}_cleaned_level_4.csv"))
#          )
#write_rds(cleaned_level_4, here("cleaned_data", str_glue("{Sys.Date()}_cleaned_level_4.rds"))
#          )


#write.csv(cleaned_level_3, here("cleaned_data", str_glue("{Sys.Date()}_cleaned_level_3.csv"))
#          )
#write_rds(cleaned_level_3, here("cleaned_data", str_glue("{Sys.Date()}_cleaned_level_3.rds"))
#          )


write.csv(cleaned_full_data, here("cleaned_data", "archive", str_glue("{Sys.Date()}_cleaned_full_data.csv"))
          )
write_rds(cleaned_full_data, here("cleaned_data", "archive", str_glue("{Sys.Date()}_cleaned_full_data.rds"))
          )
write.csv(cleaned_full_data, here("cleaned_data", "latest_cleaned_full_data.csv")
          )
write_rds(cleaned_full_data, here("cleaned_data", "latest_cleaned_full_data.rds")
          )
openxlsx::write.xlsx(cleaned_full_data, 
                     here("cleaned_data", "latest_cleaned_full_data.xlsx")
                     )


# write.csv(chem_index2, here("Output",'Chemical index.csv'), row.names = FALSE)
openxlsx::write.xlsx(chem_index2, here("Output",'chem_index_supplementary.xlsx'))



#write_rds(ref_index, here("cleaned_data", str_glue("ref_index.rds"))
#          )


```

## Condensed dataframe for Shiny app

this next chunk creates a dataframe that only contains the relevant info for the shiny, making it load quicker

``` {r shiny database}

cols <- c("refid",
          "citation",
          "year",
          "population",                                                                           
          "gender",                                                                               
          "risk",                                                                                 
          "risk_special",                                                                        
          "risk_maternal",                                                                       
          "risk_paternal",                                                                        
          "risk_compartor_group",                                                                 
          "age_exp" ,                                                                             
          "age_exp_infant",                                                                       
          "chem_name_shiny" , 
          "age_health"   ,                                                                        
          "age_health_infant" ,                                                                 
          "health_outcomes_shiny",
          "study_design",
          "country_last_author",
          "country_investigated",  
          "class",                                                                      
          "level0",
          "level1" ,         
          "group"
          )

gender_index <- data.frame(pop_gend = c("Prenatal",
                                        "Neonate",
                                        "Infant",
                                        'Child',
                                        'Adolescent',
                                        'Unsure/Not given',
                                        'Adult', 
                                        'Older adult/Elderly',
                                        'Unclear/Not given'
                                        ),
                           fig_gend = c("Prenatal (<0)",
                                        "Neonate (0-1 mnth)",
                                        "Infant (1-12 mnth)", 
                                        'Child (1-10 yrs)',
                                        'Adolescent (10-18 yrs)',
                                        'Unsure/Not given (<18 yrs)',
                                        'Adult', 
                                        'Older adult/Elderly',
                                        'Unclear/Not given'
                                        ),
                           gend_grp = c(rep('Pre- and perinatal', 2), 
                                        rep("Pre-adult (<18 yrs)", 4), 
                                        rep('Adult (>18yrs)', 3)
                                        )
                           )

shiny_df <- cleaned_full_data %>% janitor::clean_names() %>% 
  select(one_of(cols)) %>%
  unique() %>% 
  mutate(level0= case_when(
    str_detect(level0, "08 Nervous system"                                              ) ~ "Nervous system",
    str_detect(level0, "13 Disorders of the digestive system"                           ) ~ "Digestive system",
    str_detect(level0, "Health-related measures not related to a specific system"       ) ~ "Non system specific",
    str_detect(level0, "14 Disorders of the skin"                                       ) ~ "Skin",
    str_detect(level0, "16 Disorders of the genitourinary system"                       ) ~ "Genitourinary system",
    str_detect(level0, "02 Neoplasms"                                                   ) ~ "Neoplasms",
    str_detect(level0, "11 Circulatory system"                                          ) ~ "Circulatory system",
    str_detect(level0, "19 Certain conditions originating in the perinatal period"      ) ~ "Perinatal period",
    str_detect(level0, "18 Pregnancy, childbirth or the puerperium"                     ) ~ "Pregnancy, childbirth, or puerperium",
    str_detect(level0, "04 Immune system"                                               ) ~ "Immune system",
    str_detect(level0, "06 Mental, behavioural or neurodevelopmental disorders"         ) ~ "Mental, behavioural, or neurodevelopmental",
    str_detect(level0, "05 Endocrine, nutritional or metabolic disorders"               ) ~ "Endocrine, nutritional, or metabolic",
    str_detect(level0, "03 Blood or blood-forming organs"                               ) ~ "Blood or blood-forming organs",
    str_detect(level0, "12 Respiratory system"                                          ) ~ "Respiratory system",
    str_detect(level0, "09 Visual system"                                               ) ~ "Visual system",
    str_detect(level0, "10 Ear or mastoid process"                                      ) ~ "Ear or mastoid process",
    str_detect(level0, "15 Disorders of the musculoskeletal system or connective tissue") ~ "Musculoskeletal or connective tissue",
    str_detect(level0, "20 Developmental anomalies"                                     ) ~ "Developmental anomalies",
    str_detect(level0, "17 Conditions related to sexual health"                         ) ~ "Sexual health",
    str_detect(level0, "01 Certain infectious or parasitic diseases"                    ) ~ "Infectious or parasitic",
    str_detect(level0, "07 Sleep-wake disorders"                                        ) ~ "Sleep-wake")
  ) %>% 
  mutate(risk_special  = replace(risk_special,  risk_special == "", NA),
         risk_maternal = replace(risk_maternal, risk_maternal == "", NA),
         risk_paternal = replace(risk_paternal, risk_paternal == "", NA)
         ) %>%
  unite("risk_spec", 
        c(risk_special, risk_maternal,risk_paternal), 
        remove = T, 
        na.rm = T) %>%
  separate_rows(risk_spec, 
                sep = "_") %>%
  mutate(risk_group = case_when(str_detect(risk_spec, "Paternal") ~ "Paternal",
                                str_detect(risk_spec, "Maternal") ~ "Maternal",
                                str_detect(risk_spec, "Special") ~ "Individual",
                                str_detect(risk, "No") ~ "None"
                                )
         ) %>%
  unique() %>%
  mutate(risk_spec = case_when(str_detect(risk_spec, "ingestion") ~ "Ingestion",
                               str_detect(risk_spec, "occupational") ~ "Occupational",
                               str_detect(risk_spec, "other") ~ "Other (location)",
                               TRUE ~ "No special risk")
         ) %>%
  mutate(age_exp           = trimws(str_replace_all(age_exp, " \\(.*?\\)", "")),
         age_exp_infant    = trimws(str_replace_all(age_exp_infant, " \\(.*?\\)", "")),
         age_health        = trimws(str_replace_all(age_health, " \\(.*?\\)", "")),
         age_health_infant = trimws(str_replace_all(age_health_infant, " \\(.*?\\)", ""))) %>%
  mutate(age_exp    = str_replace(age_exp, "Neonate/Infant/Child/Adolescent", "Underage"),
         age_health = str_replace(age_health, "Neonate/Infant/Child/Adolescent", "Underage")) %>%
  unite("age_exp_comb", 
        c(age_exp, age_exp_infant), 
        remove = T)%>%
  unite("age_health_comb", 
        c(age_health, age_health_infant), 
        remove = T) %>% 
  separate_rows(age_exp_comb, 
                sep = "_"
                ) %>%
  separate_rows(age_health_comb, 
                sep = "_"
                ) %>%
  filter(age_exp_comb    != "") %>%
  filter(age_exp_comb    != "Underage")%>%
  filter(age_health_comb != "") %>%
  filter(age_health_comb != "Underage")%>%
  # left_join(gender_index, by = c("age_exp_comb" = "pop_gend")) %>% 
  unique() 



  
write.csv(shiny_df, here("Output",'shiny_df_condensed.csv'))
write_rds(shiny_df, here("Output",'shiny_df_condensed.rds'))
openxlsx::write.xlsx(shiny_df, here("Output",'shiny_df_condensed.xlsx'))
```

## Supplementary table

here we create the dataframe that is used as supplementary to the paper

``` {r supplementary database}


names(cleaned_full_data)

cols <- c("refid",
          "citation",
          "year",
          "country_first_auth",
          "country_last_author",
          "country_investigated",
          "population",                                                                           
          "gender",                                                                                  
          "risk_special",                                                                        
          "risk_maternal",                                                                       
          "risk_paternal",                                                                        
          "risk_compartor_group",                                                                 
          "age_exp" ,                                                                             
          "age_exp_infant", 
          "chem_name_shiny",                                                                     
          "class",  
          "multiple_exposures",                                                             
          "age_health",                                                                        
          "age_health_infant" ,                                                                 
          "health_outcomes_shiny",
          "level0",                                                                     
          "level1",                                                                    
          "group",
          "study_design")

          
supp_df <- cleaned_full_data %>%
  select(one_of(cols)) %>%
  group_by(refid, 
           population, 
           gender, 
           age_exp) %>%
  mutate(group                 = replace_na(group, "Other"),
         health_outcomes_shiny = paste(unique(health_outcomes_shiny), collapse = '; '),
         chem_name_shiny       = paste(unique(chem_name_shiny), collapse = '; '),
         level0                = paste(unique(level0), collapse = '; '),
         class                 = paste(unique(class), collapse = '; '),
         level1                = paste(unique(level1), collapse = '; '),
         group                 = paste(unique(group), collapse = '; '),
         multiple_exposures    = str_replace(multiple_exposures, 
                                             "'multiple exposures measu.+", 
                                             "Yes"),
         country_investigated  = str_replace_all(country_investigated, 
                                                "_", 
                                                "; "),
         risk_special          = replace(risk_special, risk_special == "", NA),
         risk_maternal         = replace(risk_maternal, risk_maternal == "", NA),
         risk_paternal         = replace(risk_paternal, risk_paternal == "", NA),
         age_exp_infant        = replace(age_exp_infant, age_exp_infant == "", NA),
         age_health_infant     = replace(age_health_infant, age_health_infant == "", NA),
         age_exp               = replace(age_exp, age_exp == "", NA),
         age_health            = replace(age_health, age_health == "", NA)
         ) %>%
  rename(comparator_group = risk_compartor_group
         ) %>%
  unite(
    "special_risk",
    contains("risk_"), 
    sep = "; ",
    na.rm = TRUE
    ) %>%
  unite(
    "age_exp",
    contains("age_exp"), 
    sep = "_",
    na.rm = TRUE
    ) %>%
  unite(
    "age_health",
    contains("age_health"), 
    sep = "_",
    na.rm = TRUE)
  
    
supp_df1 <- supp_df %>%
  group_by(refid,
           population,
           gender,
           age_exp
           ) %>%
  separate_rows(age_exp, 
                sep = "_"
                ) %>%
  mutate(age_exp = replace(age_exp, 
                           age_exp == "Neonate/Infant/Child/Adolescent (&lt;18)", 
                           NA)
         ) %>%
  filter(!is.na(age_exp)
         ) %>%
  mutate(age_exp = paste(unique(age_exp), 
                         collapse = '; ')
         ) %>%
  separate_rows(age_health, 
                sep = "_"
                ) %>%
  mutate(age_health = replace(age_health, 
                              age_health == "Neonate/Infant/Child/Adolescent (&lt;18)",
                              NA)
         ) %>%
  filter(!is.na(age_health)
         ) %>%
  mutate(age_health = paste(unique(age_health), 
                            collapse = '; ')
         ) %>%
  unique()%>%
  mutate(special_risk       = replace(special_risk, special_risk == "", "No"),
         multiple_exposures = replace(multiple_exposures, multiple_exposures == "", "No"),
         comparator_group   = replace(comparator_group, comparator_group == "", "NA"),
         special_risk       = str_replace_all(special_risk, 
                                              "&ndash;", 
                                              "-"),
         special_risk       = str_replace_all(special_risk, 
                                              "_", 
                                              "; "),
         age_exp            = str_replace_all(age_exp, 
                                              "&lt;", 
                                              "<"),
         age_health         = str_replace_all(age_health, 
                                              "&lt;", 
                                              "<"),
         age_exp            = str_replace_all(age_exp, "Unclear/Not given", "Neonate/Infant/Child/Adolescent (<18)"),
         age_health         = str_replace_all(age_health, "Unclear/Not given", "Neonate/Infant/Child/Adolescent (<18)") 
         ) %>%
  rename(
    "Reference ID"                       = refid, 
    "Reference citation"                 = citation, 
    "Year"                               = year,
    "Country of first author"            = country_first_auth,
    "Country of last author"             = country_last_author,
    "Country of investigated population" = country_investigated,
    "Population type"                    = population,
    "Sex"                                = gender,
    "Special risk of exposure"           = special_risk,
    "Comparator group"                   = comparator_group,
    "Age at exposure"                    = age_exp,
    "Plastic chemicals"                  = chem_name_shiny,                                                                     
    "Chemical class"                     = class,   
    "Multiple exposures"                 = multiple_exposures,                                                             
    "Age at health outcome measure"      = age_health,   
    "Health outcome measures"            = health_outcomes_shiny,
    "ICD level 0"                        = level0,                                                                     
    "ICD level 1"                        = level1,                                                                    
    "Health outcome measure sub-groups"  = group,
    "Study design"                       = study_design
    )



write.csv(supp_df1, 
          here("Output",'supplementary_data_format.csv'), 
          row.names = FALSE)

```